WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-06 method/sec_4-db_struct.tex
v5.0
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if us

\section{\acrshort{wdias} Database Structure}
\label{se:db_struct}

@@

Based on the above interpretation, a timeseries have data points ordered in time. Other than that, timeseries have additional information that is known as \emph{timeseries metadata}, which can use to identify one timeseries from another uniquely. As an example, we can place a weather station on a \emph{location}, and it can measure different types of weather data that are called \emph{parameters} such as temperature, precipitation, and wind direction. Each parameter can produce different timeseries. Even we can use the location as metadata to identify the timeseries, but that is not enough to distinctly identify the parameters. Thus we need to use a set of attributes to identify a timeseries uniquely. In the next \cref{subse:timeseries_key_attributes}, we describe key attributes that are used by the \acrshort{wdias} to identify a timeseries uniquely.

@@

\paragraph{Location}-- Location of the timeseries. All locations have a unique String identifier called \emph{locationId}. Further, two types of location types are interested in the \acrshort{wdias}, namely:
\begin{itemize}
  \item \emph{Point locations}-- Contains a name that is human readable. lat and lon of the location on the earth surface.
  \begin{lstlisting}[language=Python, lastline=-1]
    {
        "locationId": "wdias-hanwella",
        "name": "Hanwella",
        "lat": 6.909722222,
        "lon": 80.08166667
    }
  \end{lstlisting}
  \item \emph{Regular Grid locations} -- Contains a name that is human readable. The grid presents by dividing into equal size cells. Thus, it needs the number of rows and columns. 
  And the location of the first cell and the width and height of it.
  \begin{lstlisting}[language=Python]
      {
        "locationId": "wdias_kelani_basin",
        "description": "Kelani Basin",
        "rows": 120,
        "columns": 139,
        "geoDatum": "Kandawala",
        "gridFirstCell": {
            "firstCellCenter": {
                "x": 397074.0,
                "y": 504875.0
            },
            "xCellSize": 250.0,
            "yCellSize": 250.0
        }
    }
  \end{lstlisting}
  \item \emph{Irregular Grid locations} -- (endpoints are available within the WDIAS system, but skipped since it is out of the interest of the scope.)
\end{itemize}

@@

It is difficult to search for the timeseries data if those are stored over multiple data sources and trying to avoid having duplicates. Thus it adds low overhead to have a single data source to look into while searching for the timeseries metadata. The efficiency of searching for timeseries metadata can increase by using a caching mechanism. To support search queries with lower latency, we used an index for the fast search for timeseries metadata, and a geo-based index to support geo-based search queries.

Many modern database systems give a higher performance on a specific type of application. Thus, we need to use the correct database system based on application requirements. Considering the aforementioned database requirements, we can not get all of the benefits using a single general database system available. Thus we created a database structure after carefully choosing database systems per the system requirements and combining their capabilities. According to the design principle of microservices architecture, we created microservice for each of the valueType. Here we followed the concept of \emph{database per service} as described in in \cref{subse:database_per_service}. In \cref{sebse:wdias_microservices}, those microservices are grouped as \emph{adapters} that share an \acrshort{api} to interact with while keeping the persistent data private.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrfull{netCDF}}
\label{subse:netcdf}

>>>>

\section{WDIAS Database Structure}
\label{se:db_struct}

@@

Based on the above interpretation, a timeseries have data points ordered in time. Other than that, timeseries have additional information that is known as \emph{timeseries metadata}, which can use to identify one timeseries from another uniquely. As an example, we can place a weather station on a \emph{location}, and it can measure different types of weather data that are called \emph{parameters} such as temperature, precipitation, and wind direction. Each parameter can produce different timeseries. Even we can use the location as metadata to identify the timeseries, but that is not enough to distinctly identify the parameters. Thus, we need to use a set of attributes to identify a timeseries uniquely. In the next \cref{subse:timeseries_key_attributes}, we describe key attributes that are used by the \acrshort{wdias} to identify a timeseries uniquely.

@@

\paragraph{Location}-- Location of the timeseries. All locations have a unique String identifier called \emph{locationId}. Further, two types of location types are interested in the \acrshort{wdias}, namely:
\begin{itemize}
  \item \emph{Point locations}-- Contains a name that is human readable. lat and lon of the location on the earth surface.
\begin{lstlisting}[language=Python]
{
    "locationId": "wdias-hanwella",
    "name": "Hanwella",
    "lat": 6.909722222,
    "lon": 80.08166667
}
\end{lstlisting}
  \item \emph{Regular Grid locations} -- Contains a name that is human readable. The grid presents by dividing into equal size cells. Thus, it needs the number of rows and columns. 
  And the location of the first cell and the width and height of it.
\begin{lstlisting}[language=Python]
{
    "locationId": "wdias_kelani_basin",
    "description": "Kelani Basin",
    "rows": 120,
    "columns": 139,
    "geoDatum": "Kandawala",
    "gridFirstCell": {
        "firstCellCenter": {
            "x": 397074.0,
            "y": 504875.0
        },
        "xCellSize": 250.0,
        "yCellSize": 250.0
    }
}
\end{lstlisting}
  \item \emph{Irregular Grid locations} -- (endpoints are available within the WDIAS system, but skipped since it is out of the interest of the scope.)
\end{itemize}

@@

It is difficult to search for the timeseries data if those are stored over multiple data sources and trying to avoid having duplicates. ,it adds low overhead to have a single data source to look into while searching for the timeseries metadata. The efficiency of searching for timeseries metadata can increase by using a caching mechanism. To support search queries with lower latency, we used an index for the fast search for timeseries metadata, and a geo-based index to support geo-based search queries.

Many modern database systems give a higher performance on a specific type of application. Thus, we need to use the correct database system based on application requirements. Considering the aforementioned database requirements, we cannot get all of the benefits using a single general database system available. Thus, we created a database structure after carefully choosing database systems per the system requirements and combining their capabilities. According to the design principle of microservices architecture, we created microservice for each of the valueType. Here we followed the concept of \emph{database per service} as described in in \cref{subse:database_per_service}. In \cref{sebse:wdias_microservices}, those microservices are grouped as \emph{adapters} that share an \acrshort{api} to interact with while keeping the persistent data private.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Network Common Data Form}
\label{subse:netcdf}

### 2020-05-06 method/sec_5-data_preprocess.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

The data imported via import modules may have incorrect data, missing data, and incompatible data which can not directly feed into simulation modules.
Thus we need to preprocess imported data before using it for forecasting. The WDIAS supports data preprocessing capabilities via the extension modules. The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation, but users can add more extensions as required.

@@

\subsection{Interpolation}
The interpolation module generates data at desired locations or at desired data points using a serial The interpolation module generates data at desired locations or desired data points using a serial or spatial interpolation technique. It is used to fill gaps in on-line measured data and to derive spatially distributed data for weather time series, such as precipitation and temperature, based on information available at nearby locations.

\paragraph{Serial Interpolation}-- During serial interpolation, we use interpolation to fill any gaps in a time series. The interpolation module will only consider a single time series, which is itself in filling these gaps.

@@

\paragraph{Spatial Interpolation}-- During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new time series for a location using data from other (spatially distributed) locations. Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/spatial_interpolation.jpg}
    \caption{Spatial interpolation.}
    \label{fi:spatial_interpolation}
\end{figure}

>>>>

The data imported via import modules may have incorrect data, missing data, and incompatible data which cannot directly feed into simulation modules.
Thus, we need to preprocess imported data before using it for forecasting. The WDIAS supports data preprocessing capabilities via the extension modules. The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation, but users can add more extensions as required.

@@

\subsection{Interpolation}
The interpolation module generates data at desired locations or at desired data points using a serial The interpolation module generates data at desired locations or desired data points using a serial or spatial interpolation technique. It is used to fill gaps in on-line measured data and to derive spatially distributed data for weather timeseries, such as precipitation and temperature, based on information available at nearby locations.

\paragraph{Serial Interpolation}-- During serial interpolation, we use interpolation to fill any gaps in a timeseries. The interpolation module will only consider a single timeseries, which is itself in filling these gaps.

@@

\paragraph{Spatial Interpolation}-- During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations. Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/spatial_interpolation.jpg}
    \caption{Spatial interpolation.}
    \label{fi:spatial_interpolation}
\end{figure}

### 2020-05-06 method/sec_7-summary.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

Throughout this Chapter, we discussed the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}. We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}. In order to take the full advantage of using the microservices architecture, we moved to container orchestration based architecture rather than building tightly coupled microservices with the actor model. 
While implementing the import and export modules, those modules followed the microservice architecture style of \emph{smart endpoints and dumb pipes}. Each microservice is implemented as a containerized application that can deploy independent of other microservices. Also, we used the microservice architecture pattern of \emph{database per service} by combining different types of database systems to create the \acrshort{wdias} database structure. Further, we provided a comprehensive extension module system that allows users to preprocess data by creating new triggers without any downtime for system configuration. We used a geo indexing mechanism to support Geo search queries and indexed the timeseries metadata to support the search for any timeseries in \acrshort{wdias}.

>>>>

Throughout this Chapter, we discussed the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}. We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}. To take the full advantage of using the microservices architecture, we moved to container orchestration based architecture rather than building tightly coupled microservices with the actor model. 
While implementing the import and export modules, those modules followed the microservice architecture style of \emph{smart endpoints and dumb pipes}. Each microservice is implemented as a containerized application that can deploy independent of other microservices. Also, we used the microservice architecture pattern of \emph{database per service} by combining different types of database systems to create the \acrshort{wdias} database structure. Further, we provided a comprehensive extension module system that allows users to preprocess data by creating new triggers without any downtime for system configuration. We used a geo indexing mechanism to support Geo search queries and indexed the timeseries metadata to support the search for any timeseries in \acrshort{wdias}.

### 2020-05-06 results/sec_2-workload.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

We used 250 locations from Google’s Countries Public Data set \cite{GoogleGoogleCounties}, and considered static throughout the testing. For each location, we created four timeseries metadata by using four different values for the moduleId key attribute. Thus combining all together first, we created 1000 timeseries metadata during the performance test and then stored the timeseries data against timeseries unique identifiers. We have written automated scripts to generate these data for the performance testing, and scripts are generic enough to create more timeseries metadata by changing the configurations.

@@

With the above JMeter test plans, we have to enable each test plan separately and before running with JMeter distributed mode. In order to make the process faster, we implemented a script tool to interact with the JMeter test stored files. The script is available within the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev} and supports the following features.

@@

\begin{table}[ht]
\centering
\caption{\acrshort{eks} nodes}
\footnotesize
\begin{tabular}{|l|c|c|c|c|l|}
\hline
\textbf{Node Label} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \textbf{EC2 Name} \\ \hline
core & 16 & 32 & 15 & 1 & c5.4xlarge \\ \hline
grid & 8 & 16 & 25 & 1 & c5.2xlarge \\ \hline
scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\ \hline
test & 4 & 10.5 & 5 & 1 & c5n.xlarge \\ \hline
\end{tabular}
\label{tab:aws_eks_nodes}
\end{table}
\dbc{Center table on page}
\gkc{FIXED}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance Tuning}
\label{se:performance_tuning}
According to \cref{tab:aws_eks_nodes}, we selected a few physical nodes with different resource capacities. The grid and test labeled nodes have higher network bandwidth. To get better performance using the available resources, we can schedule each microservice into a predefined set of nodes. Thus we tried to deploy all JMeter microservices on test labeled nodes since the test plans need to interact with all the services and transfer bulk timeseries data. Also, the grid microservices are hosted inside the grid labeled node due to the massive size of grid data timeseries that need to be transferred during the load testing. There are few ways to assign microservice to a particular physical node in the \acrshort{k8s};

@@

Users can use one of the above methods to schedule microservice on physical nodes for better performance. For the moment, we used node affinity to schedule the microservices. We chose the above method since it allows us to schedule all the microservices in a node when there is only a single physical node available. Microservices are assigned to each node in \cref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core} -- metadata, extensions, query, status and extension services
    \item \emph{grid} -- grid adapter, import and export grid data
    \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
    \item \emph{test} --  JMeter and metric server
\end{itemize}
\cref{fi:eks_node_setup} shows the overview of the microservices assignment to each node in the \acrshort{eks} setup. Further, it shows the connectivity of the nodes and the data interactions via the arrows. We scheduled the microservices in the core labeled node together, since most of those services are communicating together, and running them inside one physical node reduces the latency. Then we separate scalar and vector microservices and their databases, in order to separate the load from the core node while storing scalar and vector timeseries data. As same as, we assigned microservices to grid and test nodes based on the higher bandwidth requirements.

>>>>

We used 250 locations from Google’s Countries Public Data set \cite{GoogleGoogleCounties}, and considered static throughout the testing. For each location, we created four timeseries metadata by using four different values for the moduleId key attribute. Thus, combining all together first, we created 1000 timeseries metadata during the performance test and then stored the timeseries data against timeseries unique identifiers. We have written automated scripts to generate these data for the performance testing, and scripts are generic enough to create more timeseries metadata by changing the configurations.

@@

With the above JMeter test plans, we have to enable each test plan separately and before running with JMeter distributed mode. To make the process faster, we implemented a script tool to interact with the JMeter test stored files. The script is available within the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev} and supports the following features.

@@

\begin{table}[ht]
\centering
\caption{\acrshort{eks} nodes}
\footnotesize
\begin{tabular}{|l|c|c|c|c|l|}
\hline
\textbf{Node Label} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \textbf{EC2 Name} \\ \hline
core & 16 & 32 & 15 & 1 & c5.4xlarge \\ \hline
grid & 8 & 16 & 25 & 1 & c5.2xlarge \\ \hline
scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\ \hline
test & 4 & 10.5 & 5 & 1 & c5n.xlarge \\ \hline
\end{tabular}
\label{tab:aws_eks_nodes}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance Tuning}
\label{se:performance_tuning}
According to \cref{tab:aws_eks_nodes}, we selected a few physical nodes with different resource capacities. The grid and test labeled nodes have higher network bandwidth. To get better performance using the available resources, we can schedule each microservice into a predefined set of nodes. Thus, we tried to deploy all JMeter microservices on test labeled nodes since the test plans need to interact with all the services and transfer bulk timeseries data. Also, the grid microservices are hosted inside the grid labeled node due to the massive size of grid data timeseries that need to be transferred during the load testing. There are few ways to assign microservice to a particular physical node in the \acrshort{k8s};

@@

Users can use one of the above methods to schedule microservice on physical nodes for better performance. For the moment, we used node affinity to schedule the microservices. We chose the above method since it allows us to schedule all the microservices in a node when there is only a single physical node available. Microservices are assigned to each node in \cref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core} -- metadata, extensions, query, status and extension services
    \item \emph{grid} -- grid adapter, import and export grid data
    \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
    \item \emph{test} --  JMeter and metric server
\end{itemize}
\cref{fi:eks_node_setup} shows the overview of the microservices assignment to each node in the \acrshort{eks} setup. Further, it shows the connectivity of the nodes and the data interactions via the arrows. We scheduled the microservices in the core labeled node together, since most of those services are communicating together, and running them inside one physical node reduces the latency. Then we separate scalar and vector microservices and their databases to separate the load from the core node while storing scalar and vector timeseries data. As same as, we assigned microservices to grid and test nodes based on the higher bandwidth requirements.

### 2020-05-06 results/sec_3-observations.tex
v5.0
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if us

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 60min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_60_min_summary}
\end{table}
Insert timeseries performed over scalar and vector data types with each request sent with 24 data points. On average, it took 28ms to insert scalar and vector data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms. Noticeably it has 0\% of errors, which means that all the requests completed successfully. Also, \acrshort{wdias} handled 40.5 \acrshort{rps} of scalar and vector data requests with the given workload. The retrieval of scalar and vector timeseries has lesser delay than the insertion.
On the other hand, insert grid timeseries data performed within 23ms, and almost all the requests perform within the same amount of time. Hence the standard deviation is smaller. Delay with inserting grid timeseries smaller because those requests are handled asynchronously. Retrieve grid timeseries data performed with a bit higher value of latency of 68ms due to performed the retrieve request on-demand. Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time during the load test.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes of data with enabled auto-scaling - Latency against server hits}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for K8s. According to the graph, the \acrshort{wdias} was able to keep the latency constant all over the elapsed time.
When compared to \cref{fi:test_obs_all_15m_latency} without auto-scaling, we can see lesser latency spikes throughout the test period.

@@

\cref{tab:obs_query_15_min_summary} shows the response latency summary details. The average latency is much higher than the minimum value. Also, the summary reported higher maximum values as well. Standard deviation showed a quiet higher value, which means the response latency values are not closer to the average value. Noticeably, we can not see any errors in the table, which means all the requests successfully process. The throughput is similar among all the requests. The performance of the adapter-query depends on the performance of the document storage database performance and geo-indexing performance.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
    \caption{Load testing query test over 5 minutes - Response Latency over Time}
    \label{fi:test_obs_query_5m_response_latency}
\end{figure}
\cref{fi:test_obs_query_5m_response_latency} shows the response latency overtime for the query test plan. When the number of requests gets higher, the latency also gets increased. Further, \cref{fi:test_obs_query_5m_response_times_vs_threads} shows the response latency against the number of active threads for the query test plan. When the number of server hits gets higher, the latency also increases. According to the Figures, we can conclude that the performance of the adapter-query depends on the database. Even if we increase the number of adapter-query pods, the throughput of the microservice is not going to increase until we increase the performance by using the z-axis scaling of scale cube concept.

>>>>

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 60min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_60_min_summary}
\end{table}
Insert timeseries performed over scalar and vector data types with each request sent with 24 data points. On average, it took 28ms to insert scalar and vector data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms. Noticeably it has 0\% of errors, which means that all the requests completed successfully. Also, \acrshort{wdias} handled 40.5 \acrshort{rps} of scalar and vector data requests with the given workload. The retrieval of scalar and vector timeseries has lesser delay than the insertion.
On the other hand, insert grid timeseries data performed within 23ms, and almost all the requests perform within the same amount of time. Hence, the standard deviation is smaller. Delay with inserting grid timeseries smaller because those requests are handled asynchronously. Retrieve grid timeseries data performed with a bit higher value of latency of 68ms due to performed the retrieve request on-demand. Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time during the load test.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}
    \caption{Load testing with 15 minutes of data with enabled auto-scaling - Latency against server hits}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for K8s. According to the graph, the \acrshort{wdias} was able to keep the latency constant all over the elapsed time.
When compared to \cref{fi:test_obs_all_15m_latency} without auto-scaling, we can see lesser latency spikes throughout the test period.

@@

\cref{tab:obs_query_15_min_summary} shows the response latency summary details. The average latency is much higher than the minimum value. Also, the summary reported higher maximum values as well. Standard deviation showed a quiet higher value, which means the response latency values are not closer to the average value. Noticeably, we cannot see any errors in the table, which means all the requests successfully process. The throughput is similar among all the requests. The performance of the adapter-query depends on the performance of the document storage database performance and geo-indexing performance.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
    \caption{Load testing query test over 5 minutes - Response Latency over Time}
    \label{fi:test_obs_query_5m_response_latency}
\end{figure}
\cref{fi:test_obs_query_5m_response_latency} shows the response latency overtime for the query test plan. When the number of requests gets higher, the latency also gets increased. Further, \cref{fi:test_obs_query_5m_response_times_vs_threads} shows the response latency against the number of active threads for the query test plan. When the number of server hits gets higher, the latency also increases. According to the figures, we can conclude that the performance of the adapter-query depends on the database. Even if we increase the number of adapter-query pods, the throughput of the microservice is not going to increase until we increase the performance by using the z-axis scaling of scale cube concept.

### 2020-05-06 results/sec_4-discussion.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

This section concludes the observations in \cref{se:observations} section against the performance metrics defined in \cref{subse:test_plan_metrics}.

@@

Adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled. However, it has some performance issues as well as memory leak issues. Since each microservice in the \acrshort{wdias} is independent of technology, we can use a different technology stack to implement the service. Doing so, we can increase the performance as an example by directly porting the adapter-grid to netCDF with a low-level language such as C or FORTRAN. Other than \acrshort{eks}, users can use a different \acrshort{k8s} cluster that supports Persistent Volumes with the access of Read Write Many \cite{LinuxFoundationPersistentKubernetes}. Then they can run multiple pods of adapter-grid and increase the throughput of handling grid data.

>>>>

This section concludes the observations in \cref{se:observations} against the performance metrics defined in \cref{subse:test_plan_metrics}.

@@

Adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled. However, it has some performance issues, as well as memory leak issues. Since each microservice in the \acrshort{wdias} is independent of technology, we can use a different technology stack to implement the service. Doing so, we can increase the performance as an example by directly porting the adapter-grid to netCDF with a low-level language such as C or FORTRAN. Other than \acrshort{eks}, users can use a different \acrshort{k8s} cluster that supports Persistent Volumes with the access of Read Write Many \cite{LinuxFoundationPersistentKubernetes}. Then they can run multiple pods of adapter-grid and increase the throughput of handling grid data.

### 2020-05-06 summary/sec_1-conclusions.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

To enhance the accuracy of the weather prediction, we need to provide reliable and timely weather data for NWMs. Even though there are many weather data integration systems, most of them are proprietary or closed source. Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customized. Also, most of the existing systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems. However, most of the concepts are outdated with the technology advancement, and we can not get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations.

>>>>

To enhance the accuracy of the weather prediction, we need to provide reliable and timely weather data for NWMs. Even though there are many weather data integration systems, most of them are proprietary or closed source. Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customized. Also, most of the existing systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems. However, most of the concepts are outdated with the technology advancement, and we cannot get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations.
